Draft Research pt3

### 2019-03-16 draftResearch_pt3.Rmd
Completed join fixes

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

@@

```{r}
yahoo <- readRDS('data/players_position_eligibility.Rds') %>%
  select(name.full, display_position, positions)

@@

df_raw <- fangraphs %>%
  full_join(yahoo, by = c("Name" = "name.full"))

```

```{r}
df_raw %>%
  filter(is.na(display_position)) %>%
  select(Name, positions, ADP, ovrl_rank, z_sum) %>%
  head(25)

df_raw %>%
  filter(Name == "Jose Ramirez") %>%
  select(Name, positions, ADP, ovrl_rank, z_sum) %>%
  head()

fangraphs %>%
  count()
```

### To Do
1. Missing joins in yahoo data (i.e. Jose Ramirez) due to inconsistent accent marks on letters (and maybe other causes too?)
2. Develop tiers of players (linear model? nearest neighbor?)
3. Replacement level stuff (new section)
4. Take averages of multiple projection sources? 
5. Build team stats based on selections, available players per round?

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tidyverse.quiet=TRUE)
require(tidyverse)
require(fuzzyjoin)
```

@@

```{r}
yahoo <- readRDS('data/players_position_eligibility.Rds') %>%
  select(name.full, display_position, positions) %>%
  mutate(name.full = chartr("áéóíñú", "aeoinu", name.full))

yahoo$name.full[yahoo$name.full == 'Daniel Vogelbach'] <- "Dan Vogelbach"
yahoo$name.full[yahoo$name.full == 'Shohei Ohtani (Batter)'] <- "Shohei Ohtani"
yahoo$name.full[yahoo$name.full == 'Shin-soo Choo'] <- "Shin-Soo Choo"
yahoo$name.full[yahoo$name.full == 'Seunghwan Oh'] <- "Seung Hwan Oh"
yahoo$name.full[yahoo$name.full == 'JT Riddle'] <- "J.T. Riddle"
yahoo$name.full[yahoo$name.full == 'AJ Reed'] <- "A.J. Reed"

@@

fangraphs$Name[fangraphs$Name == 'Enrique Hernandez'] <- "Kike Hernandez"
fangraphs$Name[fangraphs$Name == 'Cedric Mullins II'] <- "Cedric Mullins"
fangraphs$Name[fangraphs$Name == 'Michael Soroka'] <- "Mike Soroka"
fangraphs$Name[fangraphs$Name == 'Nathaniel Lowe'] <- "Nate Lowe"
fangraphs$Name[fangraphs$Name == 'Nathan Karns'] <- "Nate Karns"
fangraphs$Name[fangraphs$Name == 'Zach Britton'] <- "Zack Britton"
fangraphs$Name[fangraphs$Name == 'Joshua James'] <- "Josh James"
fangraphs$Name[fangraphs$Name == 'D.J. Stewart'] <- "DJ Stewart"

df_join <- fangraphs %>%
  full_join(yahoo, by = c("Name" = "name.full"))

df_join %>% 
  count(is.na(display_position) & is.na(positions))
```

#### Orphaned Records after join fixes
1. Replaced accented characters to characters without accents
2. Fuzzy join
3. Yahoo API query for *2500* players (rather than 850)
4. Duplicate Shohei Ohtani records, lack of pitching projections
5. Multiple player minor name mismatches

### To Do
1. Develop tiers of players (linear model? nearest neighbor?)
2. Replacement level stuff (new section)
3. Take averages of multiple projection sources? 
4. Build team stats based on selections, available players per round?
